Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-17 doc/GMP2015/s03_drp.tex
Minor changes to sec:DRP.

\begin{proof}
Note that, by definition, $d(F_i)=k$ and $d(F_j)=k$. Also, $d(F_i\cap F_j)=d(F_i)+d(F_j)-d(F_i\cup F_j)$.
\begin{enumerate}
    \item By definition of trivial graph; if $F_i\cup F_j$ were trivial, then $F_i$ and $F_j$ must be trivial.

    \item \textit{Forward direction:} Since $F_i\cup F_j$ is under-constrained and a subgraph of well-constrained $F$, it must be that $d(F_i\cup F_j)=l<k$. Therefore $d(F_i\cap F_j)=2k-l>k$. This means $F_i\cap F_j$ is trivial. \textit{Reverse direction:} We know that $d(F_i\cap F_j)>k$ because it is trivial. By the same math, we find that $d(F_i\cup F_j)<k$, showing it is under-constrained.

    \item \textit{Forward direction:} We have that $d(F_i\cup F_j)=k$, therefore $d(F_i\cap F_j)=k$. Being a subgraph of well-constrained $F$, $F_i\cap F_j$ is also well-constrained. \textit{Reverse direction:} By the same math, we find that $d(F_i\cup F_j)=k$ and, since it is also a subgraph of $F$, it is well-constrained.

    \item Subgraphs of well-constrained graph $F$ can only be trivial, under-constrained, or well-constrained. So it follows from the above that an under-constrained intersection is not possible.
\end{enumerate}
\end{proof}

@@

\begin{proof}
%I wouldn't do the forward and backward direction italics, or say proof by contradiction. Just start the first paragraph with Suppose C_i union C_j is well constained maximal proper and assume it is not C.
Assume $C_i\cup C_j \neq C$, then we just found a larger proper subgraph and the children were not vertex-maximal to begin with.

In the reverse direction, we know $C$ is either some non-leaf node (well-constrained by definition of a DR-plan) or $G$ itself (well-constrained by definition of the problem). Thus, $C_i\cup C_j$ is well-constrained.
\end{proof}

@@

\subsection{Algorithm}
The algorithm to find the optimal DR-plan is a straightforward application of the theory. It begins by finding the well-constrained vertex-maximal proper subgraphs of the input well-constrained graph. If the intersection of any two of the subgraphs is well-constrained, then take those two to be children of the graph. Otherwise, all the subgraphs are the children. Apply recursively to the children. This naturally terminates when you reach trivial subgraphs.

>>>>

\begin{proof}
Note that, by definition, $d(F_i)=k$ and $d(F_j)=k$. Also, $d(F_i\cap F_j)=d(F_i)+d(F_j)-d(F_i\cup F_j)$.
\begin{enumerate}
    \item If $F_i\cup F_j$ were trivial, then $F_i$ and $F_j$ must be trivial, by definition.

    \item Observe that under-constrained subgraphs of well-constrained graphs must have density less than $k$. Then it is straightforward application of the equation above.

    % \item Observe that, given a well-constrained graph, an under-constrained subgraph must have density less than $k$. Then it is straightforward application of the equation above.

    \item Observe that, given a well-constrained graph, a subgraph with density $k$ must also be well-constrained. Then it is straightforward application of the equation above.

    % \item \textit{Forward direction:} Since $F_i\cup F_j$ is under-constrained and a subgraph of well-constrained $F$, it must be that $d(F_i\cup F_j)=l<k$. Therefore $d(F_i\cap F_j)=2k-l>k$. This means $F_i\cap F_j$ is trivial. \textit{Reverse direction:} We know that $d(F_i\cap F_j)>k$ because it is trivial. By the same math, we find that $d(F_i\cup F_j)<k$, showing it is under-constrained.

    % \item \textit{Forward direction:} We have that $d(F_i\cup F_j)=k$, therefore $d(F_i\cap F_j)=k$. Being a subgraph of well-constrained $F$, $F_i\cap F_j$ is also well-constrained. \textit{Reverse direction:} By the same math, we find that $d(F_i\cup F_j)=k$ and, since it is also a subgraph of $F$, it is well-constrained.

    \item Subgraphs of a well-constrained graph can only be trivial, under-, or well-constrained. All cases are already exhausted.
\end{enumerate}
\end{proof}

@@

\begin{proof}
%I wouldn't do the forward and backward direction italics, or say proof by contradiction. Just start the first paragraph with Suppose C_i union C_j is well constained maximal proper and assume it is not C.
Assume $C_i\cup C_j \neq C$, then we just found a larger proper subgraph and $C_i,C_j$ were not vertex-maximal to begin with.

In the reverse direction, we know $C$ is either some non-leaf node (well-constrained by definition of a DR-plan) or $G$ itself (well-constrained by definition of the problem). Thus, $C_i\cup C_j=C$ is well-constrained.
\end{proof}

@@

\subsection{Algorithm}
\todo{Cut this section out?}
The algorithm to find the optimal DR-plan is a straightforward application of the theory. It begins by finding the well-constrained vertex-maximal proper subgraphs of the input well-constrained graph. If the intersection of any two of the subgraphs is well-constrained, then take those two to be children of the graph. Otherwise, all the subgraphs are the children. Apply recursively to the children. This naturally terminates when you reach trivial subgraphs.
